Stable Hot Spot Analysis (Draft)

### 2017-06-17 paper-main.tex
Updated Blur and Aggregation

The results can be found in Figure~\ref{fig:Zoom}. It can be seen that with an
increase of the aggregation level the values increase. 
%TODO: there was some todo in the text for the following sentence
If clusters
increase/decrease For the upward property, $G^*$ is always better than Focal
$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
reaches the same result as $G^*$ at aggregation level~5 . For the downward
property, Focal $G^*$ leads to better results at aggregation level~5.

@@

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{eqnarray*}
    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_{41}) \\
    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_{41})
  \end{eqnarray*}
\begin{displaymath}
i \in [0,11], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
shown in the first row, with increasing size. The 2nd and 3th row show how
$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that an
increase of the weight size leads in general to better results for Focal $G^*$.

>>>>

The results can be found in Figure~\ref{fig:Zoom}. It can be seen that with an
increase of the aggregation level the values increase. 
If the aggregation level increases the number of cluster decreases. It can seen that
small clusters are disappearing and some clusters are growing to big ones. From aggreagtion level~2 to
aggreagtion level~3 there is no big change in the images of Focal $G^*$ which is consitent with our results.
For the upward property, $G^*$ is always better than Focal
$G^*$, compared to the results from figure \ref{fig:SoHZoom}. Focal $G^*$
reaches the same result as $G^*$ at aggregation level~6 . For the downward
property, Focal $G^*$ leads to better results at aggregation level~6.

@@

\subsection{Blur}
We also made an example for the variation of the weight size W.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{eqnarray*}
    child & = & G^*(R_3, W_{7+i \cdot 2}, st, F_{41}) \\
    parent & = & G^*(R_3, W_{7+(i+1)\cdot 2}, st, F_{41})
  \end{eqnarray*}
\begin{displaymath}
i \in [0,11], G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Figure~\ref{fig:Blur}. The weight matrix is
shown in the first row, with increasing size. The 2nd and 4th row show how
$G^*$ and Focal $G^*$ changes based on W. This example is a slice plane of the
weight dimension ploted in figure ~\ref{fig:SoHWeight}. It can be seen that an
increase of the weight size leads in general to better results for $G^*$.
Also it can bee seen that for focal $G^*$ the clusters are more distributed over the raster.
